\documentclass[12pt,letterpaper]{article}
\usepackage{preamble}
\usepackage{tabularx}
\begin{document}

\section*{Topic: 3.1 Classifying and Drawing Triangles}
\begin{enumerate}[label=\arabic*.]
    \item Define a triangle concisely. What are not examples of triangles?
    \item Based on the name, what do you think an equilateral triangle is? Draw an equilateral triangle, what do you notice about their sides and angles?
    \item Draw an isosceles triangle, what do you notice about their sides and angles?
    \item Draw an scalene triangle, what do you notice about their sides and angles?
    \item Draw examples of equilateral, isosceles, and scalene triangles.
    \item Draw examples of right angles, acute angles, and obtuse angles
    \item Draw a right triangle, acute triangle, and obtuse triangle.
    \item There are now 9 permutations of acute, right, and obtuse vs equilateral, isosceles, scalene, are all 9 possible to draw? Use geometric markings appropriately.

          \begin{tabularx}{0.95\textwidth} {
                  | >{\centering\arraybackslash}X
                  | >{\centering\arraybackslash}X
                  | >{\centering\arraybackslash}X |}
              \hline
              Equilateral Acute Triangle\vspace{25mm} & Equilateral Right Triangle & Equilateral Obtuse Triangle \\
              \hline
              Isosceles Acute Triangle\vspace{25mm}   & Isosceles Right Triangle   & Isosceles Obtuse Triangle   \\
              \hline
              Scalene Acute Triangle\vspace{25mm}     & Scalene Right Triangle     & Equilateral Obtuse Triangle \\
              \hline
          \end{tabularx}
    \item A triangle on a coordinate plane is made up of points $A(0, 2)$, $B(5, 1)$, and $C(-3, -5)$.
          \begin{itemize}
              \item Find the lengths of $\overline{AB}$, $\overline{BC}$, and $\overline{AC}$.
              \item Based on the side lengths, is the triangle equilateral, isosceles, or scalene?
              \item Looking at the triangle, does it appear to be acute, right, or obtuse? How can you prove it? (Use Slope.)
          \end{itemize}
\end{enumerate}
\end{document}