\documentclass[12pt,letterpaper]{article}
\usepackage{preamble}
\usepackage{tabularx}
\begin{document}

\section*{Topic: 3.5 Triangle Congruence Proofs Introduction}
\begin{enumerate}
    \item Write a simple recipe for a PB\&J sandwich.
          \begin{itemize}
              \item What do you notice about the recipe's structure?
              \item Do the order of the steps matter? Explain.
              \item Think about the recipes for other foods you enjoy. What do they all boil down to?
          \end{itemize}
    \item Draw two triangles for each of the five congruence shortcuts and note any observations. Use geometric markings appropriately.

          \begin{tabularx}{0.95\textwidth} {
                  | >{\centering\arraybackslash}X
                  | >{\centering\arraybackslash}X
                  | >{\centering\arraybackslash}X |}
              \hline
              Side Angle Side (SAS)\vspace{25mm}  & Drawing & Characteristics \\
              \hline
              Side Angle Angle (SAA)\vspace{25mm} & Drawing & Characteristics \\
              \hline
              Side Side Side (SSS)\vspace{25mm}   & Drawing & Characteristics \\
              \hline
              Angle Side Angle (ASA)\vspace{25mm} & Drawing & Characteristics \\
              \hline
              Hypotenuse Leg (HL)\vspace{25mm}    & Drawing & Characteristics \\
              \hline
          \end{tabularx}
    \item Look at your observations and think back to your recipe from Q1. What similarities do you notice between these two?
    \item Could you prove that two triangles are congruent based on their characteristics? Draw two triangles and attempt this task.

\end{enumerate}
\end{document}