\documentclass[12pt,letterpaper]{article}
\usepackage{preamble}
\usepackage{tabularx}
\begin{document}

\section*{Topic: 2.3 Algebraic Proofs}
\begin{enumerate}
    \item Yesterday we saw a lot of examples of algebraic properties that we assume are true. State each of them concisely.
          \begin{itemize}
              \item Addition Property of Equality
              \item Subtraction Property of Equality
              \item Multiplication Property of Equality
              \item Division Property of Equality
              \item Commutative Property over Addition
              \item Commutative Property over Multiplication
              \item Associative Property over Addition
              \item Associative Property over Multiplication
              \item Distributive Property over Addition
              \item Transitive Property
              \item Reflexive Property
          \end{itemize}
    \item Notice in the list above the commutative, associative properties and missing subtraction and division. Does there exist a commutative and associative property over subtraction? What about division? Here's some examples to think about. Determine whether these are true or false.
          \begin{itemize}
              \item $8-2=2-8$ If you are clever, there is a way to rewrite it so it works out.
              \item $8\div2=2\div8$
              \item $(3-8)-2=3-(8-2)$
              \item $(3\div8)\div2=3\div(8\div2)$
          \end{itemize}
    \item Notice for the distributive property it is only addition. Would the 'Distributive property over Subtraction, Multiplication, and Division' hold? Here are some examples to think about. Determine whether these are true or false.
          \begin{itemize}
              \item $3(8-2)=3\cdot8-3\cdot2$
              \item $3(8\cdot2)=3\cdot8\cdot3\cdot2$
              \item $3(8\div2)=3\cdot8\div3\cdot2$
          \end{itemize}
    \item Write a two column proof (refer to yesterday's exploration) to solve the following: $$3x+5=6x+17$$
    \item Write a two column proof (refer to yesterday's exploration) to solve the following: $$4(x-5)=1+(99+x)$$

\end{enumerate}
\end{document}