\documentclass[12pt,letterpaper]{article}
\usepackage{preamble}
\usepackage{tabularx}
\begin{document}

\section*{Topic: 2.5 Parallel Lines and Angles}
\begin{enumerate}
    \item Draw a pair of parallel lines that take up the upper half of your page.
    \item Now draw a line that intersects both parallel lines, this is called a transversal. You should have 8 angles present. Label them 1-8. Just for convenience, I'll have everyone label the same way. Check-in with Mr. Freeman (or the diagram on the board).
    \item For convenience, let's use the following notation: $(a,b)$ represent angles $a$ and $b$. What can you say about $(1,2)$? What about $(1,3)$?
    \item Which angles are congruent?
    \item Which angles are supplementary?
    \item Which angles are complimentary?
    \item See if you can recall these words, and label which of your angles satisfies the angle relationships in the table. Copy this table for your notebook.\\\\
          \begin{tabularx}{0.95\textwidth} {
                  | >{\raggedright\arraybackslash}X
                  | >{\centering\arraybackslash}X
                  | >{\raggedleft\arraybackslash}X |}
              \hline
              Name of Angle Relationship (Include a mini-drawing above name) & \vspace{2mm}Angles & Complimentary, Supplementary, or Congruent \\
              \hline
              \vspace{5mm}Vertical Angles\vspace{5mm}                        &                    &                                            \\
              \hline
              \vspace{5mm}Corresponding Angles\vspace{5mm}                   &                    &                                            \\
              \hline
              \vspace{5mm}Alternate Interior\vspace{5mm}                     &                    &                                            \\
              \hline
              \vspace{5mm}Alternate Exterior Angles\vspace{5mm}              &                    &                                            \\
              \hline
              \vspace{5mm}Same Side Interior Angles\vspace{5mm}              &                    &                                            \\
              \hline
              \vspace{5mm}Same Side Exterior Angles\vspace{5mm}              &                    &                                            \\
              \hline
          \end{tabularx}
\end{enumerate}
\end{document}