\documentclass[12pt,letterpaper]{article}
\usepackage{preamble}
\usepackage{tabularx}
\begin{document}

\section*{Topic: 2.8 Equations of Parallel and Perpendicular Lines}
\begin{enumerate}
    \item Draw an example of parallel lines.
    \item If you were to determine the slope of both lines you drew, what would you predict?
    \item Draw an example of perpendicular lines.
    \item If you were to determine the slope of both lines you drew, what would you predict?
    \item Graph two equations with the same slope. Write their equations. What do you notice?
    \item Is it possible for these two equations to intersect? How do you know?
    \item Show algebraically that these two equations cannot intersect.
    \item There is actually one way for these two equations to intersect, but it is trivial. \\Can you determine when?
    \item Parallel lines have what kind of slopes and y-intercepts?
    \item Let's physically count rise over run, graph the equation: $y=\dfrac{3}{5}x+2$.
    \item At the point $(5,5)$ now graph a line that is perpendicular to that line, be exact, and use a ruler. What do you notice about the slope of that line?
    \item Perpendicular lines have what kind of slopes and y-intercepts?
    \item We are going to see a lot of problems asking about $ax+by=c$. Convert $2x+3y=5$ to slope-intercept form $y=mx+b$.
    \item I claim that we do not have to convert all standard form equations $ax+by=c$ to slope-intercept form if we can do it generally/use structure. Convert $ax+by=c$ to slope-intercept form. Determine the slope and the $y$-intercept in terms of $a$, $b$, and $c$.
    \item The slope only depends on what?
    \item Compare the equations $3x+4y=5$ and $3x+4y=7$, do you think they are parallel or perpendicular? Could you tell without solving for slope-intercept form and graphing?
    \item What about $3x+4y=5$ and $-3x-4y=7$? Are they parallel or perpendicular? Could you tell without solving for slope-intercept form and graphing?
    \item Compare the equations $3x+4y=5$ and $-4x+3y=7$, do you think they are parallel or perpendicular? Could you tell without solving for slope-intercept form and graphing?
    \item Can you generalize? If I have two equations in form of $y=mx+b$ or $ax+by=c$ when will those equations be parallel? Perpendicular?
\end{enumerate}
\end{document}