\documentclass[12pt,letterpaper]{article}
\usepackage{preamble}
\usepackage{tabularx}
\begin{document}

\section*{Topic: 1.2 Geometric Markings and Segment Addition Postulate}
\begin{enumerate}
    \item What do you think is the difference between a theorem, theory, law, and postulate? (There are more, such as lemma, axiom, postulate).
    \item Draw a line segment, measure its length. Now copy the same line segment and break it up into two pieces. Measure their lengths. What do you notice?
    \item Repeat the same thing but break the line segment into three pieces. What do you notice?
    \item Draw an example of congruent lines.
    \item Draw an example of parallel lines.
    \item Draw an example of perpendicular lines.
    \item Draw an example of congruent angles.
    \item Draw an example of right angles.
    \item The letter "A" features what kind of lines?
    \item The letter "E" features what kind of lines?
    \item The letter "H" features what kind of lines?
    \item The letter "K" features what kind of lines?
    \item The letter "L" features what kind of lines?
    \item The letter "M" features what kind of lines?
    \item The letter "N" features what kind of lines?
    \item The letter "T" features what kind of lines?
    \item The letter "V" features what kind of lines?
    \item The letter "W" features what kind of lines?
    \item The letter "X" features what kind of lines?
    \item The letter "Y" features what kind of lines?
    \item The letter "Z" features what kind of lines?
    \item What letters from this list are somewhat unlike? Why aren't some letters included?
    \item What do you think midpoint means?
\end{enumerate}

\end{document}